\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{helvet}
\usepackage{changepage}
\usepackage{multicol} % Add this to your preamble
\renewcommand{\familydefault}{\sfdefault}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
    pdfauthor={Le Dinh Phung},
    pdftitle={Curriculum Vitae}
}


\definecolor{maincolor}{RGB}{0,76,153}

\titleformat{\section}
  {\color{maincolor}\Large\bfseries}
  {}{0em}{}
\titleformat{\subsection}
  {\color{maincolor}\normalsize\bfseries}
  {}{0em}{}

\begin{document}

\begin{center}
    {\Huge\bfseries\color{maincolor} Le Dinh Phung} \\[0.5em]
    \href{https://phung-portfolio-nvim.vercel.app}{My Portfolio}

\end{center}

\vspace{1em}

\section{Personal Information}
\begin{adjustwidth}{2em}{}
\textbf{Name:} Le Dinh Phung

\textbf{Email:} \href{mailto:ledinhphung25082000p@gmail.com}{ledinhphung25082000p@gmail.com}

\textbf{GitHub:} \href{https://github.com/shegga9x}{My Git}

\textbf{Phone:} 0382508253
\end{adjustwidth}

\section{Summary}
\begin{adjustwidth}{2em}{}
\textbf{Backend Developer} specializing in \textbf{Java} and \textbf{Spring Boot}. Experienced in building \textbf{scalable applications}, integrating authentication systems, and optimizing database performance. Proficient in \textbf{Next.js} for frontend, and familiar with AWS OpenSearch. Recently expanding expertise in \textbf{microservices architecture}, Docker, and Nginx for deployment and orchestration.
\end{adjustwidth}

\section{Experience}
\begin{adjustwidth}{2em}{}
\textbf{FJS System} (Internship - 4 months)
\begin{itemize}[leftmargin=*]
    \item Gained hands-on experience in backend development using \textbf{Java} and \textbf{Struts}.
\end{itemize}
\end{adjustwidth}

\section{Technical Skills}
\begin{adjustwidth}{2em}{}
\begin{itemize}[leftmargin=*]
    \item \textbf{Programming:} Java (Spring, Java Core), JavaScript (Next.js)
    \item \textbf{Backend:} Spring Boot, Spring Security, OAuth2, Struts
    \item \textbf{Frontend:} Next.js, React
    \item \textbf{Databases:} MySQL
    \item \textbf{Version Control:} Git, GitHub
    \item \textbf{Cloud/Deployment:} AWS (EC2, RDS, S3, Tebi), Vercel
\end{itemize}
\end{adjustwidth}

\newpage

\section{Projects}
\begin{adjustwidth}{2em}{}
\begin{multicols}{2}

% First column: Social Media App (AppF4)
\subsection{Social Media App (AppF4)}

\textbf{GitHub:} \href{https://github.com/shegga9x/appf4}{AppF4 Repository}

% \textbf{Live Demo:} Backend - \href{http://appf4.io.vn}{appf4.io.vn}, Frontend - \href{http://social.appf4s.io.vn}{social.appf4s.io.vn}

\textbf{Overview:} A social media platform developed with a team of four to explore microservices and micro frontends. My role: backend architecture, deployment workflow, and integration of enterprise-grade technologies.

\textbf{Key Contributions:}
\begin{itemize}[leftmargin=*]
    \item Designed a scalable backend using JHipster microservices and Spring Boot.
    \item Set up production deployment workflow with Docker, Nginx, and VPS.
    \item Implemented Liquibase for automated DB migrations.
    \item Integrated Keycloak for centralized authentication and role-based access.
    \item Configured Jenkins pipelines for automated CI/CD.
    \item Initiated integration of Kafka and Elasticsearch.
\end{itemize}

\textbf{Technologies Used:}
\begin{itemize}[leftmargin=*]
    \item Backend: JHipster, Spring Boot, Kafka, Redis, Consul, Liquibase
    \item Frontend: Microfrontend with React
    \item Database: PostgreSQL
    \item DevOps \& CI/CD: Docker, Nginx, VPS, Jenkins
\end{itemize}

\end{multicols}

\begin{center}
    \rule{0.8\textwidth}{0.5pt}
\end{center}

\begin{multicols}{2}

% Second column: Book Store Application & Antoree E-Learning Platform

\subsection{Book Store Application}

\textbf{GitHub:} \href{https://github.com/shegga9x/book-store-app}{BookStore Repository}

\textbf{Technologies:} Java, Spring Boot, Next.js, AWS Services (EC2, RDS, S3, Tebi), GHN, VNPay

\textbf{Key Features:}
\begin{itemize}[leftmargin=*]
    \item Developed advanced book sorting and filtering functionalities.
    \item Implemented secure authentication with \textbf{OAuth2}.
    \item Built a \textbf{scalable cloud-based infrastructure} on AWS, supporting up to \textbf{2 million book records}.
    \item Integrated online payment via \textbf{VNPay} and shipping services with \textbf{GHN}.
    \item Planned optimization of search queries using Elasticsearch.
\end{itemize}

\vspace{1em}

\subsection{Antoree E-Learning Platform}

\textbf{GitHub:} \href{https://github.com/phungle2508/Antoree-Intern-Project}{Antoree Repository}

\textbf{Live Demo:} \href{https://antoree-intern-project.vercel.app}{antoree-intern-project.vercel.app}

\textbf{Technologies:} Next.js, Tailwind CSS, AI Chat

\textbf{Overview:} Developed a modern E-Learning platform template featuring smart course recommendations powered by AI chat. The project leverages Next.js and Tailwind CSS for rapid development and responsive design.

\textbf{Key Features:}
\begin{itemize}[leftmargin=*]
    \item AI-powered chat for personalized course recommendations.
    \item Modern, responsive UI built with Next.js and Tailwind CSS.
    \item Template designed for scalability and easy integration of new features.
\end{itemize}

\end{multicols}
\end{adjustwidth}

\end{document}